\section{Discussion}\label{sec:discussion}

\subsection{Summary of Findings}

Our investigation highlights several consistent patterns across task domains and encoding modalities:

\paragraph{Strong domain-dependent effects.}
The four domains separate into a consistent difficulty hierarchy: control near ceiling,
classification strong, regression moderate, and bandit hardest.
This pattern is stable across FW (det.) analyses and indicates that task
geometry---not just model capacity---is the main determinant of OOD generalization quality.

\paragraph{Direct baseline comparison reveals meta-learning value.}
The No-adapt MLP provides a strong sanity check on meta-learning necessity.
On regression it achieves negative $R^2$ ($-1.786$), failing to provide useful predictive structure; FW (det.)'s advantage is clear.
On control the No-adapt MLP achieves $R^2 = 0.790$, capturing shared qualitative structure (stabilization via negative feedback) but missing task-specific geometry.
FW (det.)'s $+25.9\%$ improvement reflects genuine task adaptation beyond family-level prototyping.

\paragraph{Oracle collapse: what structural information decoders need.}
One of the most diagnostic findings is oracle mode's poor performance: providing perfect task identification (one-hot family index) yields only $16.7\%\pm14.3\%$ win-rate.

This does not mean ``perfect encoding but failed decoding.''
Rather, it means task identity is categorically different from task structure.
Oracle carries categorical information (``this is family X''); support and text carry structural information (``this task has these dynamics, these input-output relationships, this semantic intent'').
In our setting, the decoder does not reliably convert categorical labels into useful weights because labels carry little structural signal---no input-output examples, no dynamics, no features.

\paragraph{What encodings provide that oracle does not.}
Support demonstrations: observed input-output pairs, implicit task dynamics, sample diversity.
Text descriptions: semantic task intent, relevant variables, control objectives.
Hybrid: both structural sources.
Oracle: family identity only.

The oracle result suggests that \emph{general-purpose fast weight generation benefits from structural task information}, not just labels.
Demonstration and text modes survive (text $26.4\%$ vs oracle $16.7\%$) because they provide structural features the decoder can exploit.

\paragraph{Encoding modality shapes decoder utilization.}
Despite oracle collapse, encoding modality profoundly affects performance.
Text achieves best reward ($26.4\%\pm6.1\%$) despite substantially lower reconstruction ($R^2 = 0.770 \pm 0.029$) than support ($0.971 \pm 0.007$).
Encoding modality shapes which structural signals the decoder prioritizes: demonstrations enable input-output mapping; language enables task semantics.
Yet the reconstruction--reward gap persists across all modalities, indicating an important limitation of the current decoder setup.
No single modality closes the gap.

\subsection{Limitations}

\paragraph{Training scale.}
All experiments use only 1000 gradient steps per stage with batch size 32.
At this scale the encoder is likely under-trained; Figure~\ref{fig:support_sweep} suggests performance is still improving at larger support sizes, and training curves show no clear convergence.
Results at 1000 steps should be interpreted as a lower bound on the system's capability.

\paragraph{Task complexity.}
Current tasks are synthetic 2D toy problems.
Target networks are small (13K parameters, 2-dimensional input), latent codes are 32-dimensional, and dynamics are low-dimensional continuous systems.
Transferring findings to higher-dimensional tasks (e.g.\ image-based tasks, high-DoF robotics) requires significant architectural scaling.

\paragraph{Reward evaluation protocol.}
The reward win-rate metric is sensitive to the strength of the No-adapt MLP comparator.
In our protocol, the No-adapt MLP is a well-tuned task-agnostic learned policy; a weaker comparator would inflate win-rates for all modes.
Reported win-rates below 50\% do not necessarily mean meta-learned policies are \emph{poor}---they may still achieve strong absolute reward while the comparator is unusually strong.

\paragraph{Statistical power.}
Encoding-mode ablations use only 3 seeds.
Standard deviations are substantial (e.g.\ text win-rate $\pm6.1\%$), and confidence intervals for differences between modes overlap, making definitive ranking statistically fragile.

\paragraph{Text encoder quality.}
DistilBERT is a general-purpose language model pre-trained on Wikipedia and BooksCorpus, not on task description corpora.
TaskDescription strings in our setup are concise single-sentence explanations; a fine-tuned or instruction-following LLM may extract substantially richer task structure.

\subsection{Proposed Future Experiments}

We identify the following experiments as most likely to yield significant improvements and clearer conclusions.

\paragraph{1. Long-run training (priority: high).}
Scaling to 10K--50K training steps per stage for all task types with periodic evaluation checkpoints would reveal whether the reconstruction--reward gap shrinks with training.
Our 1000-step runs are likely well below the performance ceiling for this architecture.
A full convergence study (loss curve to plateau, with held-out set evaluation every 500 steps) would establish a meaningful performance upper bound.

\paragraph{2. Reward-aware best-of-$k$ selection (priority: high).}
Currently reward audit uses a single produced policy.
Evaluating multiple candidate reconstructions per episode (via lightweight latent perturbations or ensembling) and selecting the best-reward policy with a short rollout proxy would test whether candidate diversity directly improves reward.
This is a direct intervention to close the reconstruction--reward gap without changing the core architecture.

\paragraph{3. More seeds and power analysis (priority: medium).}
Increasing from 3 to 10 seeds and running a formal two-sided $t$-test (or bootstrap confidence intervals) for mode comparisons would sharpen statistical conclusions.
At 3 seeds, the standard error on text-mode win-rate is $\pm3.5\%$, making differences non-significant.
A sample-size calculation from the observed effect sizes suggests $\geq$8 seeds are needed for 80\% power at $\alpha = 0.05$.

\paragraph{4. Latent dimension and architecture sweep (priority: medium).}
The current $d_z = 32$ latent dimension may be too compressed for high-diversity tasks.
Sweeping $d_z \in \{16, 32, 64, 128\}$ together with encoder and decoder width would characterise the expressivity--trainability frontier.
Larger latents may capture richer task families at the cost of more difficult optimization.

\paragraph{5. Harder OOD generalisation (priority: medium).}
Current OOD families are mild variants of training dynamics.
Designing \emph{structurally distinct} OOD tasks (e.g.\ chaos-inducing parameters, qualitatively different attractors, partial observability) would more rigorously probe the system's generalisation capacity rather than interpolation near training distribution boundaries.

\paragraph{6. Online / iterative adaptation (priority: medium).}
A natural extension is to use initial rollout rewards to update the latent representation in a few additional gradient steps---similar in spirit to context-conditioned meta-RL.
Starting from the encoder posterior and running a handful of reinforce-style updates on the latent code would combine the fast-weight advantage with online fine-tuning, without full model retraining.

\paragraph{7. Stronger text conditioning (priority: medium--low).}
Replacing DistilBERT with a larger instruction-following model (e.g.\ Llama-3 8B or GPT-4 via API) and writing richer task descriptions would likely improve text-mode reward transfer.
The current descriptions are one-sentence summaries; LLMs respond better to structured prompts that include state/action semantics, reward shaping details, and expected challenge.

\paragraph{8. Proper meta-learning baselines (priority: medium--low).}
Comparing against MAML, Prototypical Networks adapted to the weight-generation setting, and PEARL on the control task would contextualise whether the gains from hypernetwork generation are meaningful relative to well-tuned gradient-based meta-learners.
Currently the \emph{only} baseline is a task-agnostic MLP, which represents an ideally weak comparator.

\paragraph{9. Real-world control environments (priority: low--future).}
Transferring to standard continuous control benchmarks (MuJoCo HalfCheetah, Ant, Hopper with randomised dynamics) would establish whether the toy control findings hold at scale.
This requires scaling the target network architecture, the hypernetwork, and the support set collection procedure, but the conceptual framework is directly applicable.

\subsection{Conclusion}

The main result of this paper is not the proposal of a new framework, but the empirical finding that decoder performance depends strongly on the structure of the task encoding it receives.
Using a common encoder--hypernetwork testbed, we find that FW (det.) provides a strong reconstruction reference and encoding modality matters more than categorical task identity.
In particular, text encoding (semantic language descriptions) gives the best reward transfer in our control ablation, while oracle family identity collapses despite respectable reconstruction.
We also identify a systematic reconstruction--reward gap and provide a prioritised roadmap of experiments for understanding and potentially closing it.
