\section{Introduction}

A central challenge in machine learning is adapting quickly to new tasks from limited evidence.
Meta-learning approaches address this by learning across a distribution of tasks so that inference on a novel task requires only a small support set.
One natural instantiation is to learn a mapping from support sets to neural network weights---so-called \emph{fast weights} or \emph{hypernetworks}---which can directly produce a task-specific solver in a single forward pass without any gradient update at test time.

\paragraph{A note on fast-weight generation.}
Our focus is deterministic support-conditioned weight generation, where a single forward pass maps task evidence to target-network parameters.
The central question is which task encodings the decoder can use effectively.

\paragraph{The role of encoding modality and structural information.}
Beyond support set demonstrations, a task can be described via multiple information channels.
Practitioners combine sensor data with verbal instructions; LLM agents receive observations and language specifications; humans engage with demonstrations and natural-language task descriptions.
The critical question is: what \emph{structural properties} of task encoding enable decoder generalization?
We study four complementary modalities with distinct information profiles:
(i)~\emph{support encoding}: task demonstrations (rich input-output relationships, task-specific structure),
(ii)~\emph{text encoding}: natural-language descriptions via DistilBERT (semantic task intent, relevant variables),
(iii)~\emph{hybrid}: convex mixture of support and text (complementary structural signals),
(iv)~\emph{oracle}: perfect task identification via one-hot family index (maximum categorical information, zero structural features).
The oracle mode is theoretically revealing: it provides perfect answers to ``which family is this task?'' but zero information about ``what makes this task behave this way?''
Comparing these modes illuminates what structural properties decoders actually use for generalization.

\paragraph{This work.}
Our main goal is to study which forms of task information actually support decoder generalization.
To do so, we use an encoder--hypernetwork system as a concrete experimental vehicle that lets us compare support, text, hybrid, and oracle conditioning under a common decoder.

We evaluate systematically across classification, regression, bandit optimisation, and control tasks, and use the resulting comparisons to isolate which encoding modalities provide information the decoder can actually exploit.
Our contributions are:
\begin{enumerate}
  \item A diagnostic empirical study of what structural properties of task encoding enable decoder generalization across heterogeneous task domains.
  \item Systematic comparison of four encoding modalities (support, text, hybrid, oracle) revealing distinct trade-offs: support achieves high reconstruction ($R^2 = 0.971 \pm 0.007$), text achieves the strongest deployed reward ($26.4\%\pm6.1\%$ win-rate), and oracle performs poorly despite perfect task identification.
  \item Empirical identification of the \emph{reconstruction--reward gap}: high parameter-space $R^2$ does not guarantee deployed reward. This gap suggests decoders learn to fit parameter space without capturing task structure relevant for generalization.
  \item The oracle collapse result: perfect task identification (one-hot family index) achieves only $6.6\%\pm6.3\%$ win-rate, suggesting that task labels are insufficient on their own. In our setting, decoders benefit from structural task information (demonstrations or language descriptions) rather than categorical identity alone.
  \item A practical finding on representation choice: demonstration and hybrid encodings provide the most reliable improvements, while label-only conditioning remains fragile.
\end{enumerate}

The remainder of the paper is organised as follows.
Section~\ref{sec:related} reviews related work.
Section~\ref{sec:method} describes the experimental architecture and training procedure.
Section~\ref{sec:experiments} presents quantitative and qualitative results.
Section~\ref{sec:discussion} discusses findings, limitations, and proposed future experiments.
